The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-21 paper.tex
update

 The temperature profile (left middle panel in \Cref{fig__profile}) along the positive z-axis in\
 \Cref{fig__jetI5+ismSeed3-45deg} indicates that\
 the smooth region (red band) emitting X-ray\
 is around 0.3-0.4 keV, similar to that observed by \citet{Miller2016} and \citet{Kataoka2018}.

@@

 The most interesting finding is that there is a innermost bubbles\
 (dashed box in left top panel of \Cref{fig__jetI5+ismSeed3-45deg})\
 extending out from the GC on either side of the thin disk.\
 The innermost bubbles are cold (1-10 eV), dense ($10^{-4}$--$10^{-2}$ cm$^{-3}$),\
 and underpressured with respect to the turbulent plasma.\
 Moreover, the close-up view of profiles around $z=3.7$ kpc (right column in \Cref{fig__profile})
 demonstrates that there is a sharp pressure jump and dense shell at $z=3.61$ kpc,\
 indicating that the innermost bubbles are an expanding reverse shock.\
 We also find that the turbulent plasma is bracketed between the downstream of reverse shock\
 and of the outermost forward shock, thus heating the turbulent plasma up considerably.

@@

  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__profile.png}
    \caption{
             Left: the profiles of pressure (top), temperature (middle),\
             and number density (bottom)\
             along the positive z-axis in \Cref{fig__jetI5+ismSeed3-45deg}.
             Right: the close-up view of profiles around $z=3.7$ kpc.\
             The sharp pressure jump and dense shell at $z=3.61$ kpc\
             indicate that the innermost bubbles\
             (dashed box in top left panel of \Cref{fig__jetI5+ismSeed3-45deg})\
             are an expanding reverse shock.\
     }
    \label{fig__profile}
  \end{figure}

>>>>

 The temperature profile (left middle panel in \Cref{fig__profile}) along the positive z-axis in\
 \Cref{fig__jetI5+ismSeed3-45deg} indicates that\
 the smooth region (purple band) emitting X-ray\
 is around 0.3-0.5 keV, similar to that observed by \citet{Miller2016} and \citet{Kataoka2018}.

@@

 The most interesting finding is that there is a innermost bubbles\
 (dashed box in left top panel of \Cref{fig__jetI5+ismSeed3-45deg})\
 extending out from the GC on either side of the thin disk.\
 The innermost bubbles are cold (1-10 eV), dense ($10^{-4}$--$10^{-2}$ cm$^{-3}$),\
 and underpressured with respect to the turbulent plasma.\
 Moreover, the close-up view (right column in \Cref{fig__profile}) of profiles in yellow band
 demonstrates that there is a sharp pressure jump and dense shell at $z=3.61$ kpc,\
 indicating that the innermost bubbles are an expanding reverse shock.\
 We also find that the turbulent plasma is bracketed between the downstream of reverse shock\
 and of the outermost forward shock, thus heating the turbulent plasma up considerably.

@@

  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__profile.png}
    \caption{
             Left: the profiles of pressure (top), temperature (middle),\
             and number density (bottom)\
             along the positive z-axis in \Cref{fig__jetI5+ismSeed3-45deg}.
             Right: the close-up view of profiles in the yellow band.\
             The sharp pressure jump and dense shell at $z=3.61$ kpc\
             indicate that the innermost bubbles\
             (dashed box in top left panel of \Cref{fig__jetI5+ismSeed3-45deg})\
             are an expanding reverse shock.\
     }
    \label{fig__profile}
  \end{figure}
